The Impact of Critical Slicing in SFL\Comment{tatistical Fault Localization}

### 2018-11-10 paper/main.tex
describing lithium and its complexity

Statistical Fault Localization (\sfl{}) and Dynamic Slicing are
popular complementary approaches proposed to automate debugging.
\sfl{}~\cite{7390282} computes
suspiciousness values associated with program entities (e.g., basic
blocks) using coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in
decreasing order of suspiciousness.  \sfl{} received tremendous
attention over the years, but its applicability to support debugging
remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been shown
useful in supporting downstream analyses, such as Automated Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for likely fixes to
likely buggy statements.  Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
technique for automated debugging. It takes as input a failing test
and produces on output a set of statements--the slice--that influence
the evaluation of the fault-revealing assertion.

@@

\section{Dynamic Slicing}
\label{sec:slicing}

Program slicing is a program understanding method to identify the
relevant parts of the program with respect to given points of
interest.  This paper focuses on dynamic slicing~--~as opposed to
static slicing~\cite{Weiser:1981:PS:800078.802557}~--~for its
application in automated software
debugging~\cite{Binkley:2014:OLP:2635868.2635893}.  To select a slicer
implementation to run our experiments, we considered two criteria:
robustness as to support non-trivial programs and efficiency as to
support execution of our experiments in reasonable time.
Unfortunately, we failed to find public implementations satisfying
these criteria.

For those reasons, we decided to implement a critical slicer for Java,
which is the language of the subjects in our dataset, \dfj{}. We
focused on Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310} for
its simplicity.\Comment{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\Comment{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices\footnote{In the original implementation, critical
  slicing was not guaranteed to be executable.  Above we refer to the
  basic strategy of deleting statement and checking outcomes.}.
Critical Slicing slices the program by deleting statements such that
the sliced program preserves critical observations (\eg{}, assertion
violations).  The output we used to determine equivalence of the
original failing execution and the sliced failing execution was the
stack trace produced by the assertion violation.  It is important to
note that Binkley \etal{} recently proposed the critical slicer
ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
efficiency (important to run our experiments) for generality. Some of
the slicing jobs we ran on ORBS took hours to run. For example,
\Fix{...elaborate...}

The principle of Critical Slicing is rather simple, consisting of
mutating the program and observing the output. Despite that,
optimizations are important to make a Critical Slicing implementation
efficient. We describe the optimizations we used in the following.

@@

\vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
major cost associated with critical
slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
  of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
program schemata where every statement in function bodies is guarded
by a branch predicate to control its activation. The slicer
re-executes the program with different guard configurations, recording
the smallest slice found. It uses a local search to find the smallest
slice for a given time budget. A slice is encoded as a list of flags,
each indicating whether or not a given guard is active. The initial
configuration of a slicing job has the flags set for all statements
covered by a given test.

@@

\vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
given test is necessary in Critical Slicing. However, test
re-execution may introduce flakiness due to side-effects in data
reachable from static fields. One alternative to address this problem
is to run each test in a separate JVM. Unfortunately, that alternative
is prohibitively slow. For that, we ran the slicing job in a single
JVM, using a test runner that is able to clean the static area of the
JVM as follows. At every re-execution of the critical slicer, the test
runner creates a new instance of a custom class loader, child of the
original JVM class loader.  Before loading a class, the custom class
loader checks in a cache whether or not the bytecodes were already
loaded. If not, the class file is loaded from disk and the bytecodes
are stored in the cache for future access. If the bytecodes were
previously loaded, the slicer avoids disk access by reading the data
directly from the cache.  To sum, the use of a new class loader
enables the slicer to ``reset'' the state prior to a new execution of
the same test~---~the objects accessible from the static area become
unreachable when the class loader is disposed at the end of an
execution.

\vspace{1ex}
Our implementation is publicly available under the following link (not
anonymized): \oururl{}.

\section{\sfl}
\label{sec:sfl}

\Mar{borrowed from our ICST17 paper. needs to }

>>>>

Spectrum-Based Fault Localization (\sfl{}) and Dynamic Slicing are
popular complementary approaches proposed to automate debugging.
\sfl{}~\cite{7390282} is a statistical debugging method that computes
suspiciousness values associated with program entities (e.g., basic
blocks) using coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in
decreasing order of suspiciousness.  \sfl{} received tremendous
attention over the years, but its applicability to support debugging
remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been shown
useful in supporting downstream analyses, such as Automated Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for likely fixes to
likely buggy statements.  Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
technique for automated debugging. It takes as input a failing test
and produces on output a set of statements--the slice--that influence
the evaluation of the fault-revealing assertion.

@@

\section{Background}
\label{sec:background}

This section presents important background material for the rest of the paper.

\subsection{Critical Slicing}
\label{sec:slicing}

%% To select a slicer implementation to run our experiments, we
%% considered two criteria: robustness as to support non-trivial programs
%% and efficiency as to support execution of our experiments in
%% reasonable time.  Unfortunately, we failed to find public
%% implementations satisfying these criteria.
%% For those reasons, we decided to implement a critical slicer for Java,
%% which is the language of the subjects in our dataset, \dfj{}.

Program slicing is a program understanding method to identify the
relevant parts of the program with respect to given points of
interest.  This paper focuses on dynamic slicing\Comment{~--~as
  opposed to static slicing~\cite{Weiser:1981:PS:800078.802557}~--~}
for its application in automated software
debugging~\cite{Binkley:2014:OLP:2635868.2635893} where failing tests
exist. We focused on Critical
Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its
simplicity/generality.\Comment{ In constrast with alternative slicing
  implementations based on dependency
  chains~\cite{Tip:1994:SPS:869354}\Comment{(\eg{},
    JSlice~\cite{Wang:2004:UCB:998675.999455} and
    JavaSlicer~\cite{hammacher-bachthesis-2008})},} Critical Slicing
prescribes a black-box language-semantics-agnostic recipe to computing
executable slices.  Critical Slicing minimizes the program by deleting
statements such that the sliced program preserves critical
observations (\eg{}, assertion violations). The simplification
mechanism used in Critical Slicing is rather simple, consisting of
mutating the program and observing the output.

We used the Mozilla Lithium tool~\cite{lithium} as the implementation
for Critical Slicing. Lithium is conceptually similar to the DD-min
Delta Debugging algorithm~\cite{zeller-hildebrandt-tse2002}, but
operates on code instead of test inputs. It takes as input a file and
produces as output a simplified version of that file that satisfies a
user-defined oracle. For dynamic slicing, the oracle is defined such
that the test produces the same failure manifestation. The Lithium
minimization process starts by determining the initial size of
chunks---in number of lines---to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search
looking for chunks to remove from the file that satisfy the
oracle. When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more line can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs can be found elsewhere~\cite{lithium-complexity}.

%% Despite that, optimizations are important to
%% make a Critical Slicing implementation efficient. We describe the
%% optimizations we used in the following.

%% The output we used to determine equivalence of the original failing
%% execution and the sliced failing execution was the stack trace
%% produced by the assertion violation.  It is important to note that
%% Binkley \etal{} recently proposed the critical slicer
%% ORBS~\cite{DBLP:conf/scam/BinkleyGHIKY15}, but its design sacrifies
%% efficiency (important to run our experiments) for generality. Some of
%% the slicing jobs we ran on ORBS took hours to run. For example,
%% \Fix{...elaborate...}

@@

%% \vspace{1ex}\noindent\textbf{Single compilation.}  Recompilation is a
%% major cost associated with critical
%% slicing~\cite{DBLP:conf/scam/BinkleyGHIKY15}. For example, \Fix{...\%
%%   of time in a slicing job from ORBS is due to compilation}. For that reason, our slicer uses a
%% program schemata where every statement in function bodies is guarded
%% by a branch predicate to control its activation. The slicer
%% re-executes the program with different guard configurations, recording
%% the smallest slice found. It uses a local search to find the smallest
%% slice for a given time budget. A slice is encoded as a list of flags,
%% each indicating whether or not a given guard is active. The initial
%% configuration of a slicing job has the flags set for all statements
%% covered by a given test.

@@

%% \vspace{1ex}\noindent\textbf{Clean state execution.} Re-execution of a
%% given test is necessary in Critical Slicing. However, test
%% re-execution may introduce flakiness due to side-effects in data
%% reachable from static fields. One alternative to address this problem
%% is to run each test in a separate JVM. Unfortunately, that alternative
%% is prohibitively slow. For that, we ran the slicing job in a single
%% JVM, using a test runner that is able to clean the static area of the
%% JVM as follows. At every re-execution of the critical slicer, the test
%% runner creates a new instance of a custom class loader, child of the
%% original JVM class loader.  Before loading a class, the custom class
%% loader checks in a cache whether or not the bytecodes were already
%% loaded. If not, the class file is loaded from disk and the bytecodes
%% are stored in the cache for future access. If the bytecodes were
%% previously loaded, the slicer avoids disk access by reading the data
%% directly from the cache.  To sum, the use of a new class loader
%% enables the slicer to ``reset'' the state prior to a new execution of
%% the same test~---~the objects accessible from the static area become
%% unreachable when the class loader is disposed at the end of an
%% execution.

\subsection{Spectrum-based Fault Localization}
\label{sec:sfl}
